---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# bespokelearnr

<!-- badges: start -->
<!-- badges: end -->

This package generates bespoke learning materials for a workshop-style class that provides an introduction to the emerging field of Data Science in R, including data analysis and visualization, with a particular focus on its utility for biological insight. In class, students will be provided with biological datasets using this package, and introduced to the `tidyverse` and `code` used to examine data.

## Installation

You **cannot** yet install the released version of tidybiology from [CRAN](https://CRAN.R-project.org) with:

```{r eval=FALSE}
install.packages("bespokelearnr")
```

So in the meantime, use the development version from [GitHub](https://github.com/) with:

```{r eval=FALSE}
# install.packages("devtools")
devtools::install_github("matthewhirschey/bespokelearnr")
```
