---
title: ''
subtitle: ''
author: ''
date: ''
output: ~
learnr::tutorial:
  df_print: tibble
runtime: shiny_prerendered
---
```{r setup, include=FALSE}
library(learnr)
library(tidyverse)
library(knitr)
library(here)
library(twitterwidget)
library(rlang)
knitr::opts_chunk$set(echo = FALSE, 
                      fig.align="center")
setwd(system.file(package = "bespokelearnr"))
source("tutorials/bespokelecture/code/metadata.R") #loads dataset-specific variables
source("tutorials/bespokelecture/code/bespoke.R") #loads custom objects
```
# R <br>Integrated Development Environment
Any questions?

## R
Statistical Programming Language
```{r r_exercise, exercise=TRUE}

```
  
```{r r_image, echo=FALSE, fig.cap="", out.height = '100%'}
url <- "https://source.unsplash.com/Vb8pR6cKCRI/300×200"
knitr::include_graphics(url)
```
<font size = "1">Photo by [Photo by Evan Hein on Unsplash](https://unsplash.com/@evanheinphoto)</font>

## Rstudio
Integrated Development Environment

```{r r_de, echo=FALSE, fig.cap="", out.height = '100%'}
url <- "https://source.unsplash.com/XuDPnpox8tc/300×200"
knitr::include_graphics(url)
```
<font size = "1">[Photo by Jaromír Kavan on Unsplash](https://unsplash.com/@jerrykavan)</font>

---
[Open Rstudio](http://www.rstudio.cloud)  
<iframe src="http://www.rstudio.cloud"></iframe>

## Rstudio Demonstration
Go to code/  
Open 01_r_demo.Rmd  
Follow along.  
## `filter()` rows based on certain condition(s) {.build}

The `filter()` verb evalutes a logical statement, and if a row meets the condition of this statement (i.e. is true) then it gets chosen (or "filtered").  
  
  
**All other rows are discarded**  

## `filter()` {.build}

Filtering can be performed on **categorical** data

``r dataframe_name` %>%`     
    `filter(`r colnames(df_character_select)` == "`r df_character_filter`") %>%`     
    `head(3)`  

```{r filter_exercise, exercise=TRUE}

```

Note that `filter()` only applies to rows, and has no effect on columns

## `filter()` {.build}

Filtering can also be performed on **numeric** data

For example, if you wanted to choose `r colnames(df_numeric_select)` with a value greater than `r df_numeric_filter`, you would run the following. 

``r dataframe_name` %>%`     
    `filter(`r colnames(df_numeric_select)` > `r df_numeric_filter`) %>%`     
    `head(3)`  

```{r filter_exercise2, exercise=TRUE}

```

## `filter()` {.build}

To filter on multiple conditions, you can write a sequence of `filter()` commands

``r dataframe_name` %>%`       
    `filter(`r colnames(df_character_select)` == "`r df_character_filter`") %>%`  
    `filter(`r colnames(df_numeric_select)` > `r df_numeric_filter`) %>%`    
    `head(3)`  

```{r filter_exercise3, exercise=TRUE}

```

## `filter()` {.build}

To avoid writing multiple `filter()` commands, multiple logical statements can be put inside a single `filter()` command, separated by commas

``r dataframe_name` %>%`           
    `filter(`r colnames(df_character_select)` == "`r df_character_filter`",`  
           ` `r colnames(df_numeric_select)` > `r df_numeric_filter`) %>%`      
    `head(3)`  

```{r filter_exercise4, exercise=TRUE}

```
