## Counting strings {.build}
```{r setup_count, include=FALSE}
df_input2 %>% count(string(df_2_col), sort = TRUE) %>% slice(2) %>% select(1) %>% pull()
#restart here
```

`str_count()` is a function we can use to count the number of rows that match a particular pattern.  
  
The output with either be 1 (match), or 0 (no match)  

<div class= "red2"> Example </div>  
In this code:  
- string we want to evaluate is `r dataframe_name`$`r df_2_col`  
- pattern we want to count is "`r word1`"  

`str_count(`r dataframe_name`$`r df_2_col`, '`r word1`')`  

## Counting
`str_count(`r dataframe_name`$`r df_2_col`, '`r word1`')`

```{r str_count, exercise = TRUE}

```

## Summarizing our counts
A bunch of 0 and 1 are not incredibly useful.

But since R is good at adding, we can simply wrap the previous expression in `sum()`  

Try it below:    
```{r sum_string, exercise = TRUE}

```

## Matching subsets of strings {.build}

We previously matched the entire string "`r word1`" 
But we can use the same function to detect patterns within longer strings.  
  
`str_count(`r dataframe_name`$`r df_2_col`, '`r word2`')`

## What about subsets of strings?  
`str_count(`r dataframe_name`$`r df_2_col`, '`r word2`')`

What does the ouput mean?  
```{r str_count_exercise, exercise = TRUE}

```

## A note about string patterns

When using a stringr function, you may get an output saying a string pattern doesn't exist. If you know for sure it does, <div class="blue"> double check capitalization </div>  
  
**The string must match exactly, or it will not be found!**

## Detecting strings {.build}
In addition to counting, we can use another function `str_detect()` to logically evaluate a character string.  
  
Because this logically evaluates an expression, the output is either `TRUE or FALSE`  
  
Practially, `str_detect` is used to detect the presence or absence of a pattern in a string  

## Logic Evaluation 
<div class= "red2"> Example </div>  
Find elements in `r df_2_col` that matches "`r word2`"  

`str_detect(`r dataframe_name`$`r df_2_col`, '`r word2`')`
  
```{r strdetect, exercise=TRUE}

```

## Modifiying strings with `str_replace()` {.build}
In the case of `r df_2_col`, say we want to replace every `r word1` with "IGF1" because `r word1` is incorrect.  

`str_replace(`r dataframe_name`$`r df_2_col`, '`r word1`', 'IGF1')`

```{r str_replace, exercise=TRUE}

```

## Modifiying strings with `str_replace()` {.build}
We use this same code to  modify the `r df_2_col` column by assigning it to the same variable     
  
``r dataframe_name`$`r df_2_col` <-`       
       `str_replace(`r dataframe_name`$`r df_2_col`, '`r word1`', 'IGF1')`

```{r str_replace in col, warning = FALSE, echo=FALSE}
df_input[df_2_col] <- 
  str_replace(df_input[df_2_col], word1, "IGF1")

head(df_input[df_2_col], n = 10)
```

## Using `stringr` with `dplyr` {.build}
We can use `stringr` functions in tandem with `dplyr` functions.    
  
<div class= "red2"> Example </div>  

`new_df <-` 
  ``r dataframe_name` %>%`  
   `mutate(new_col = str_detect(`r df_2_col`, '`r word2`'))`

```{r stringr_with_dplyr, exercise=TRUE}

```
 
