## Combining datasets {.build}

There are many times when you have two or more overlapping datasets that you would like to combine

The `dplyr` package has a number of `*_join` functions for this purpose

## `left_join` {.build}

```{r left_join, echo=FALSE, fig.cap="tidyexplain by gadenbuie", out.height='66%'}
url <- "https://github.com/gadenbuie/tidyexplain/blob/master/images/left-join.gif?raw=true"
knitr::include_graphics(url)
```

## `left_join` {.build}

Returns all rows from `x`, and all columns from `x` and `y`

Rows in `x` with no match in `y` will have NA values in the new columns

If there are multiple matches between `x` and `y`, all combinations of the matches are returned

## `left_join` example {.build}

Take a look at the variables in each dataset - ``r dataframe_name`` and ``r dataframe_join_name``  

You will notice that both datasets contain a common variable - ``r colnames(df_id[1])``. This can therefore serve as a common variable to join on. Let's join on this:  
  
`left_join` ``r dataframe_name`` with ``r dataframe_join_name`` and assign the output to a new object called ``r dataframe_name`_join_left`

``r dataframe_name`_join_left <-`
      `left_join(`r dataframe_name`, `r dataframe_join_name`, by = '`r colnames(df_id[1])`')`

## `left_join` example {.build}
``r dataframe_name`_join_left <-`
      `left_join(`r dataframe_name`, `r dataframe_join_name`, by = '`r colnames(df_id[1])`')`

```{r left_join example, echo=FALSE, fig.cap="", out.height='66%'}
df_join <- left_join(df_input, df_input2, by = colnames(df_id[1]))
df_join
```


## `right_join`
```{r right_join, echo=FALSE, fig.cap="tidyexplain by gadenbuie", out.height='66%'}
url <- "https://github.com/gadenbuie/tidyexplain/blob/master/images/right-join.gif?raw=true"
knitr::include_graphics(url)
```


## `right_join` {.build}
Returns all rows from `y`, and all columns from `x` and `y`

Rows in `y` with no match in `x` will have NA values in the new columns

If there are multiple matches between `x` and `y`, all combinations of the matches are returned
  
This is conceptually equivalent to a `left_join`, but can be useful when stringing together multiple steps using %>% 

## `inner_join`
```{r inner_join, echo=FALSE, fig.cap="tidyexplain by gadenbuie", out.height='66%'}
url <- "https://github.com/gadenbuie/tidyexplain/blob/master/images/inner-join.gif?raw=true"
knitr::include_graphics(url)
```

## `inner_join` {.build}
Returns all rows from `x` where there are matching values in `y`, and all columns from `x` and `y`

If there are multiple matches between `x` and `y`, all combination of the matches are returned

## `full_join`
```{r full_join, echo=FALSE, fig.cap="tidyexplain by gadenbuie", out.height='66%'}
url <- "https://github.com/gadenbuie/tidyexplain/blob/master/images/full-join.gif?raw=true"
knitr::include_graphics(url)
```

## `full_join` {.build}
Returns all rows and all columns from both `x` and `y`  

Where there are no matching values, returns NA for the one missing  
