# R <br> Markdown
Any questions?

## Scientific Reproducibly and Provenance with
```{r rmarkdown_logo, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="", out.width='40%'}
url <- "https://github.com/rstudio/hex-stickers/raw/master/PNG/rmarkdown.png"
knitr::include_graphics(url)
```
<font size = "1">[www.rstudio.com](www.rstudio.com)</font>

## R Markdown
Plain text file with 3 types of content  
```{r rmarkdown_3parts, echo=FALSE, fig.cap="", out.width='66%'}
url <- "https://github.com/matthewhirschey/tidybiology-plusds/raw/master/media/Rmarkdown.png"
knitr::include_graphics(url)
```

## Use the 'knit' button to render a report
```{r rmarkdown_knit_button, echo=FALSE, fig.cap="", out.width='66%'}
url <- "https://d33wubrfki0l68.cloudfront.net/96ec0c54c6d64ea2ec3665db9b3b781962ff6339/5cee1/lesson-images/how-3-output.png"
knitr::include_graphics(url)
```

## How it works
```{r rmarkdown_knit, echo=FALSE, fig.cap="", out.width='66%'}
url <- "https://d33wubrfki0l68.cloudfront.net/61d189fd9cdf955058415d3e1b28dd60e1bd7c9b/b739c/lesson-images/rmarkdownflow.png"
knitr::include_graphics(url)
```
  
When you run render, R Markdown feeds the .Rmd file to knitr ⧉, which executes all of the code chunks and creates a new markdown (.md) document which includes the code and it’s output.  
  
The markdown file generated by `knitr` is then processed by `pandoc` which is responsible for creating the finished format.  
  
This may sound complicated, but R Markdown makes it extremely simple by encapsulating all of the above processing into a single render function.  
  
## Key `knitr` points {.build}
- `Knitr` runs the document in a fresh R session, which means you need to load the libraries that the document uses **in the document**  
  
- Objects made in one code chunk will be available to code in later code chunks, but not before  
  
- For example, first create `r dataframe_name` and then using `dplyr::left_join` you create `r dataframe_join_name`, `r dataframe_name` will be available later on in the document to do this. **However, you cannot use `r dataframe_join_name` in a code chunk before you make it, even if it is available in your environmnet**  
  
- To keep this straight, just think (and code) in sequential chunks

## Rmarkdown -- The definitive Guide
[https://bookdown.org/yihui/rmarkdown/](https://bookdown.org/yihui/rmarkdown/)  
<center><iframe src="https://bookdown.org/yihui/rmarkdown/"></iframe></center>

# Rmarkdown <br>Text
Any questions?  
