## COVID-19 rapidly infected people across the US
```{r covid map, echo=FALSE, fig.cap="", out.height = '50%', out.width = '50%'}
url <- "https://github.com/BAREJAA/bespokelearnr/blob/merge_essentials/inst/tutorials/bespokelecture/data/covid.gif?raw=true"
knitr::include_graphics(url)
```

## COVID-19 Data {.build}
- Infection rates (epidemiology)  
- Basic science data (sequencing, molecular biology, drug lead)  
- Translational data (pre-clinical, Phase 1, Phase 2)  
- Clinical data (Chest CT)  
- Literature (pre-print and peer reviewed)

## Rapid emergence generated several healthcare decision-making challenges {.build}
**Volume**  
- Rapid data collection & storage allowed access to huge amounts of medical information  
  
**Ubiquity**  
- Data became available anywhere across geography, social, and economic classes   
  
**Latency**  
- Technology facilitates no delay in access to data    
  
## How do you make sense of COVID-19 data to make better health care decisions? {.build}
**Data-driven** decision making!  
  
```{r hierarchy, echo=FALSE, fig.cap="", out.height = '100%'}
url <- "https://upload.wikimedia.org/wikipedia/commons/0/06/DIKW_Pyramid.svg"
knitr::include_graphics(url)
```
<font size = "1">https://en.wikipedia.org/wiki/DIKW_pyramid</font>
  
