## Labels and Legends
Several options exist to change the default labels and legends. Recall, this code:  
  
`ggplot(`r dataframe_name`, aes(x=`r df_char1_name`, y=`r df_numeric1_name`) +`  
`geom_jitter() +`    
`geom_boxplot(aes(color = `r df_char1_name`))`   

## Labels and Legends {.build}
```{r labs, echo = FALSE, warning = FALSE}
original_plot <- ggplot(df_input, aes(!!sym(df_char1_name), !!sym(df_numeric1_name))) +
  geom_jitter() +
  geom_boxplot(aes(color = !!sym(df_char1_name)))
original_plot
```
  
But it has two problems:  
1. The x-axis label is redundant  
2. The figure legend is also redundant  

## Change labels using `labs`
`ggplot(`r dataframe_name`, aes(x=`r df_char1_name`, y=`r df_numeric1_name`) +`  
`geom_jitter() +`    
`geom_boxplot(aes(color = `r df_char1_name`)) +`  
`labs(x ="") #blank quotes removes the label`

## Change labels using `labs`
Gave us this plot:  
```{r labs_fix, echo = FALSE, warning = FALSE}
ggplot(df_input, aes(!!sym(df_char1_name), !!sym(df_numeric1_name))) +
  geom_jitter() +
  geom_boxplot(aes(color = !!sym(df_char1_name))) +
  labs(x = "")
```

## Change legend using `guides`
`ggplot(`r dataframe_name`, aes(x=`r df_char1_name`, y=`r df_numeric1_name`) +`  
`geom_jitter() +`    
`geom_boxplot(aes(color = `r df_char1_name`)) +`  
`labs(x ="") #blank quotes removes the label +`  
`guides(color = "none")`

## Change legend using `guides` 
```{r guides, echo = FALSE, warning = FALSE}
lab_plot <- ggplot(df_input, aes(!!sym(df_char1_name), !!sym(df_numeric1_name))) +
  geom_jitter() +
  geom_boxplot(aes(color = !!sym(df_char1_name))) +
  labs(x = "") + 
  guides(color = "none")
original_plot + lab_plot
```
