# Rmarkdown <br>YAML
Any questions?  

## Rmarkdown header is called 'YAML'
```{r rmarkdown_yaml, echo=FALSE, fig.cap="", out.width='66%'}
url <- "https://github.com/matthewhirschey/tidybiology-plusds/raw/master/media/Rmarkdown-yaml.png"
knitr::include_graphics(url)
```

## Rmarkdown output is defined here
```{r rmarkdown_output, echo=FALSE, fig.cap="", out.width='66%'}
url <- "https://github.com/matthewhirschey/tidybiology-plusds/raw/master/media/Rmarkdown-output.png"
knitr::include_graphics(url)
```

## Rmarkdown formats
Recall that Rmarkdown documents can be rendered into several different output file types
<center><iframe src="https://rmarkdown.rstudio.com/formats.html"></iframe></center>

## Rmarkdown Parameters
Parameters of a document are defined in the YAML header, and can pre-populate an Rmarkdown document. To see this in action,  
  
1. Open 11_rmarkdown_params.Rmd.  
2. Click the dropdown menu next to Knit and use Knit with Parameters to render the document.  
3. What happens if you type in a different gender or different age?  

--- 

```{r rmarkdown_params, echo=FALSE, fig.cap="", out.width='75%'}
url <- "https://github.com/matthewhirschey/tidybiology-plusds/raw/master/media/Rmarkdown-parameters.png"
knitr::include_graphics(url)
```

--- 

```{r rmarkdown_using_params, echo=FALSE, fig.cap="", out.width='75%'}
url <- "https://github.com/matthewhirschey/tidybiology-plusds/raw/master/media/Rmarkdown-using-parameters.png"
knitr::include_graphics(url)
```

## Take another look
<h1>Re-inspect 11_rmarkdown_params.Rmd.</h1>
<br>
<br>
Where were the parameters called in the code?
