---
title: Tidybiology
subtitle: Intro to Data Science using R
author: Matthew Hirschey & Akshay Bareja
date: '2020-09-04'
output: learnr::tutorial
runtime: shiny_prerendered
---
```{r setup, include=FALSE}
library(learnr)
library(tidyverse)
library(knitr)
library(here)
library(twitterwidget)
library(rlang)
library(ggrepel)
library(viridis)
library(gghighlight)
library(patchwork)
knitr::opts_chunk$set(echo = FALSE, 
                      fig.align="center")
```

```{r load, include = FALSE}
path <- '/Users/matthewhirschey/Dropbox/DUKE/PROJECTS/bespokeDS/bespokelearnr/inst/extdata'
proteins <- readRDS(paste0(path, '/bespoke_dataframe.Rds'))
###
proteins_join <- readRDS(paste0(path, '/bespoke_dataframe_join.Rds'))
joined <- proteins %>% right_join(proteins_join, by = 'id')
###
df_input <- proteins # this line is for bespoke.R to get proper var
source('/Users/matthewhirschey/Dropbox/DUKE/PROJECTS/bespokeDS/bespokelearnr/inst/content/metadata.R')
source('/Users/matthewhirschey/Dropbox/DUKE/PROJECTS/bespokeDS/bespokelearnr/inst/content/bespoke.R')
```
## Doctors make decisions based on symptoms 
```{r intro, echo=FALSE, fig.cap="", out.height = '100%'}
url <- "https://source.unsplash.com/701-FJcjLAQ/500x500"
knitr::include_graphics(url)
```
<font size = "1">Photo by [National Cancer Institute on Unsplash](https://unsplash.com/@nci)</font>

## New digital healthcare era introduces new decision-making challenges {.build}
**Volume**  
- Data collection & storage allows access to huge amounts of medical information  
  
**Ubiquity**  
- Data are available anywhere across geography, social, and economic classes   
  
**Latency**  
- Technology facilitates no delay in access to data    
  
## How do you make better health care decisions? {.build}
**Data-driven** decision making!  
  
```{r hierarchy, echo=FALSE, fig.cap="", out.height = '100%'}
url <- "https://upload.wikimedia.org/wikipedia/commons/0/06/DIKW_Pyramid.svg"
knitr::include_graphics(url)
```
<font size = "1">https://en.wikipedia.org/wiki/DIKW_pyramid</font>
  
## Emerging field of Data Science
```{r venn1, echo=FALSE, fig.cap="", out.height= '100%'}
url <- "https://images.squarespace-cdn.com/content/v1/5150aec6e4b0e340ec52710a/1364352051365-HZAS3CLBF7ABLE3F5OBY/ke17ZwdGBToddI8pDm48kB2M2-8_3EzuSSXvzQBRsa1Zw-zPPgdn4jUwVcJE1ZvWQUxwkmyExglNqGp0IvTJZUJFbgE-7XRK3dMEBRBhUpxPe_8B-x4gq2tfVez1FwLYYZXud0o-3jV-FAs7tmkMHY-a7GzQZKbHRGZboWC-fOc/Data_Science_VD.png?format=1500w"
knitr::include_graphics(url)
```
<font size = "1">http://drewconway.com/zia/2013/3/26/the-data-science-venn-diagram</font>

## Venn Diagram of Data Science v2.0
```{r venn2, echo=FALSE, fig.cap="", out.height= '100%'}
url <- "https://3.bp.blogspot.com/-bvQxcwfqATQ/V-E_uTBc4VI/AAAAAAAAMGQ/Qa1Ntef-rs0E-mWx5pkVu-CPlREdvD0TwCLcB/s1600/VennDiagram2.png"
knitr::include_graphics(url)
```
<font size = "1">Joel Grus via KDnuggets</font>

## Overall goal is Knowledge Generation
```{r knowledge, echo=FALSE, fig.cap="", out.height = '100%'}
url <- "https://upload.wikimedia.org/wikipedia/commons/0/06/DIKW_Pyramid.svg"
knitr::include_graphics(url)
```
<font size = "1">https://en.wikipedia.org/wiki/DIKW_pyramid</font>

## Several Approaches to Knowledge Generation {.build}
- New tools allow data interrogation more easily than ever before 

```{r approaches, echo=FALSE}
tweet <- twitterwidget('1125268670324695041')
```
<center>`r tweet`</center>

## World's most popular programming languages
```{r popular, echo = FALSE}
excel <- tibble(
  name = c("Excel", "Java", "C", "C++", "Python"), 
  num = c(100000000, 9000000, 6000000, 4000000, 3000000)
)
excel_plot <- ggplot(excel) +
  geom_col(aes(x = fct_rev(fct_reorder(name, num)), y = num), fill = "navy") +
  labs(x = "", y = "Number of Users (Million)") +
  scale_y_continuous(labels = c("0", "25", "50", "75", "100")) +
  theme_minimal()
excel_plot
#need to add source
```

## Your choice in programming language {.build}
- Data scientists and programmers have strong opinions about the differences in languages  
  
- The focus here will be on the R programming language  
  
<bold>"It's not important which language you choose, but rather what you can do with it"</bold>  
    
# R <br> language
Any questions?

## R is a language
```{r language, echo=FALSE, fig.cap=""}
url <- "https://source.unsplash.com/ZzWsHbu2y80/256x455"
knitr::include_graphics(url)
```
<font size = "1">Photo by Hannah Wright on Unsplash</font>

## R has values
- 1
- "North Carolina"
- "2020-04-08"

## R has objects
- A name without quotes  
- Assigned using `<-` (looks like an arrow pointing left)  
- Can be a value, object, or function result  

## Try assigning an object 
1. Assign an object; **remember, no quotes on name**  
`name <- 4`  
  
2. Return that object by typing its name  
`name`  
  
Try this in the code chunk below, then hit "Run Code"  

```{r my_first_object, exercise=TRUE}

```

## R has functions
- A name without quotes  
- Followed by () to run the function  
- Optional arguements: values, objects, or function results  
- `round(x, digits = 3)`

Try this in the code chunk below, then hit "Run Code"  

```{r my_first_fun, exercise=TRUE}
round(pi, digits = 3)

```

## Which of these are numbers?

```{r num_quiz, echo=FALSE}
question("Which of these are numbers?",
  answer("1", correct = TRUE),
  answer('"1"', message = "Because it has quotes, it is an string"),
  answer('"one"', message = "Because it has quotes, it is an string"),
  answer("one",  message = "R recognizes this as an object"), 
  allow_retry = TRUE, 
  random_answer_order = TRUE
)
```

## Which of these will work?
Suppose `one <- 1`
```{r one_quiz, echo=FALSE}
question("Which of these will work?",
  answer("log(1)", correct = TRUE),
  answer('log("1")', message = "You cannot log transform a word (string)"),
  answer('log("one")', message = "You cannot log transform a word (string)"),
  answer("log(one)", correct = TRUE), 
  allow_retry = TRUE, 
  random_answer_order = TRUE
)
```
Try it for yourself!  
  
```{r scratchpad, exercise=TRUE}
one <- 1
```

## Data are stored in tables and dataframes
Data stored in a dataframe are conceptually equivalent to a spreadsheet with rows and columns  
  
This is a sample from the ``r dataframe_name`` dataset  
  
```{r kable}
df_input %>% 
  select(1:5) %>% 
  slice(1:5) %>% 
  knitr::kable()
```

## Data are stored in tables and dataframes
Data stored in a dataframe are conceptually equivalent to a spreadsheet with rows and columns  
  
This is a sample from the ``r dataframe_name`` dataset  
  
```{r tibble}
df_input %>% 
  select(1:5) %>% 
  slice(1:5) %>% 
  print(as_tibble())
```

## Extract or create new objects
```{r extract_setup, include=FALSE}
col <- sample(colnames(df_input), 1)
```

You can call a single part of the data frame  
  
`r dataframe_name`$`r col`

```{r extract, echo = FALSE, warning = FALSE}
df_input %>% 
  select(!!col)
```

## Extract or create new objects 
  
Write the R code required to extract a variable from the `r dataframe_name` dataset:  
  
Remember, the format is: `r dataframe_name`$`r col`  
  
```{r extract_exercise, exercise=TRUE}

```

## Extract or create new objects 
  
You can also save a part of the dataframe as an object for later use  
  
``r col` <- `r dataframe_name`$`r col``  
  
In the code chunk below:  
1. On the first line, write the R code to save a single column to a new object   
2. On the second line, type the object name - this will print out the new object  
3. Run the code  
  
```{r create_exercise, exercise=TRUE}

```
  
